Where Do Population III Stars Form?

### 2018-10-24 paper.tex

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars. Previous studies have investigated the possibility of finding Pop III systems. \citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems. Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova. Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiences > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.

Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars. \citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time. \citet{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing espcape fraction, leads to large differencies in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

>>>>

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars. Previous studies have investigated the possibility of finding Pop III systems. \citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems. Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova. Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.

Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars. \citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time. \citet{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux. We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
